\documentclass{sig-alternate}
%\usepackage{graphicx}

\begin{document}

\title{Geo-Store: A Spatially-Aware SPARQL Evaluation Engine (Demo Paper)}

\numberofauthors{3}
\author{
% 1st. author
\alignauthor
Chih-Jye Wang\\
    \affaddr{Department of CSSE}\\
    \affaddr{Auburn University}\\
    \affaddr{Auburn, AL, USA}\\
    \email{wangchj@auburn.edu}
% 2nd. author
\alignauthor
Wei-Shinn Ku\\
    \affaddr{Department of CSSE}\\
    \affaddr{Auburn University}\\
    \affaddr{Auburn, AL, USA}\\
    \email{weishinn@auburn.edu}
\alignauthor
Haiquan Chen\\
    \affaddr{Department of Math and CS}\\
    \affaddr{Valdosta State University}\\
    \affaddr{Valdosta, GA, USA}\\
    \email{hachen@valdosta.edu}
}

\conferenceinfo{GIS'12,} {November 6-9, 2012. Redondo Beach, CA,
USA}\CopyrightYear{2012}

\maketitle

\begin{abstract}
Nowadays, how to utilize spatial data on the semantic web has
attracted more and more interests from researcher due to the
rapidly increasing applications on geographic information, e.g.,
location-based services (LBS). However, there are currently
limited solutions providing efficient management of spatial data
on the semantic web. In this demonstration, we present Geo-Store,
a novel spatially-aware data management system built on the
state-of-art RDF triple store. By the augmentation of the standard
SPARQL language with spatial query filters, Geo-Store is able to
process complex queries with common spatial constraints.  Those
spatial filters are further analyzed and evaluated based on the
Spatially-Aware Hashing (SAH). In SAH, spatial data are
pre-processed and encoded with their Hilbert values by using
space-filling curves, resulting in a higher query processing
efficiency than the existing triple store approaches, with no
compromise in accuracy. Our system can be accessed at
http://ilab.auburn.edu/geostore.
\end{abstract}


\category{H.2.8}{Database Management}{Database
Application}[spatial databases and GIS]

\terms{Algorithms and Experimentation}

\keywords{Location-based services, space-filling curves, the
Semantic Web}

\input{intro}
\input{design}
\input{demo}
\input{conclusion}

%\small
\bibliographystyle{abbrv}
\bibliography{gis2012}
\balancecolumns
\end{document}
